Object-Oriented Internet - Azure Interoperability

### 2020-12-02 Latex/Manuscript.tex
Remove CV from the authors list #45
- done - fixes #45

\author{Mariusz Postół\inst{1}, Piotr Szymczak\inst{1}, Clemens Vasters\inst{2}}
\headauthor{Postół M, Szymczak P, Vasters C}
\affiliation
{
 \inst{1}Lodz University of Technology\\
 Institute of Information Technology\\
 ul. Wólczańska 215, 90-924 Lodz, Poland\\
 mailto:mariusz.postol@p.lodz.pl
 \andinst
 \inst{2}Microsoft\\
 Faculty/Department/Office Name\\
 Postal Address with the zip-code\\
 clemensv@microsoft.com
}

>>>>

\author{Mariusz Postół\inst{1}, Piotr Szymczak\inst{1}}
\headauthor{Postół M, Szymczak P, Vasters C}
\affiliation
{
 \inst{1}Lodz University of Technology\\
 Institute of Information Technology\\
 ul. Wólczańska 215, 90-924 Lodz, Poland\\
 mailto:mariusz.postol@p.lodz.pl
}
